LogChunks: A Data Set for Build Log Analysis

### 2020-01-27 msr-paper/paper.tex
insert link, cassee citation & clean up bibliography, minor abstract corrections

\author{Carolin Brandt}
\author{Annibale Panichella}
\author{Andy Zaidman}
\author{Moritz Beller}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build logs are the textual by-products that a software build processes
creates, often as part of its Continuous Integration (CI)
pipeline. Build logs are a paramount source of information for
developers when debugging into and understanding a build
failures. Recently, attempts to partly automate this time-consuming,
purely manual activity have come up, such as rule- or
information-retrieval-based techniques.

@@

\subsection{Log Collection}
In this section, we describe how we created \emph{LogChunks} along the
overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
scripts\todo{link to repo?} and highly configurable.

@@

\paragraph{Research about Build Logs}
The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests. \todo{citation pending}
%TODO Caro: nathan cassee (with Alexander Sebrenik) did this in his master thesis (paper got accepted, will get link when preprint is finished), did not find others yet that do this}.

>>>>

\author{Carolin Brandt}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}
\email{c.e.brandt@tudelft.nl}
\author{Annibale Panichella}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}
\email{a.panichella@tudelft.nl}
\author{Andy Zaidman}
\affiliation{
  \institution{Delft University of Technology}
  \country{The Netherlands}
}
\email{a.e.zaidman@tudelft.nl}
\author{Moritz Beller}
\affiliation{Inventitech}
\email{mmb@inventitech.com}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Build logs are textual by-products that a software build process
creates, often as part of its Continuous Integration (CI)
pipeline. Build logs are a paramount source of information for
developers when debugging into and understanding a build
failure. Recently, attempts to partly automate this time-consuming,
purely manual activity have come up, such as rule- or
information-retrieval-based techniques.

@@

\subsection{Log Collection}
In this section, we describe how we created \emph{LogChunks} along the
overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
scripts\footnote{Data collection scripts avaliable on GitHub: http://tiny.cc/data-collection} and highly configurable.

@@

\paragraph{Research about Build Logs}
The data from \emph{LogChunks} can support research around the topic of build logs such as how users use keywords to retrieve information about build failures from logs or how they discuss failures of CI builds within pull requests~\cite{cassee2019silent}.
